TBD

### 2016-10-13 paper.tex
very rough conjugate gradient section
started cleaning up CG section

\section{Conjugate Gradient Method}

The conjugate gradient method is an iterative method which is used to solve large linear systems, i.e.
\begin{equation}
\label{eq:linear_system}
\bb = \bA\bx,
\end{equation}
where $\bb$ is a known complex column vector, $\bx$ is the unknown complex column vector with the same length as $\bb$, and $\bA$ is a square complex matrix with appropriate dimensions.  
The conjugate gradient method can in general only be applied to the above linear system if $\bA$ is a square positive-definite or a positive semi-definite Hermitian matrix. If
$\bA$ is a square positive semi-definite Hermitian matrix, then the conjugate gradient method only converges if $\bb$ is in the column range of $\bA$ (cite Lu2016). Moreover, using the 
conjugate gradient method to solve Eq.~\eqref{eq:linear_system} will only be computationally advantageous if $\bA$ is also sparse (contain many zero entries).

The Conjugate Gradient method was independently discovered by Hestenes and Stiefel. They later published a joint paper, n, which is now considered as the seminal
reference on CG. Kaniel was able to determine convergence bounds for CG using Chebyshev polynomials. A much more in depth analysis of CG convergence was conducted 
by van erSluis and van der Vorst. [Reid is credited for popularizing CG as an iterative method that can efficiently solve large sparse linear systems] RW.

\begin{algorithm}
\caption{Conjugate Gradient Method}\label{algo:extrap_algo}
\begin{algorithmic}[1]
\State $\br \gets \bA\bx_0 - \bb$
\State $\bp \gets -\br_0$
\For{$k\leq k_{\textrm{max}}$}
\State $\alpha_k \gets \frac{\br_k^H\br_k}{\bp_k^H\bA\bp_k}$
\State $\bx_{k+1} \gets \bx_k + \alpha_k\bp_k$
\State $\br_{k+1} \gets \br_k - \alpha_k\bA\bp_k$
\If{$\|\br_{k+1}\|<\epsilon\|\br_0\|$}
\State break
\EndIf
\State $\beta_{k} \gets \frac{\br_{k+1}^H\br_{k+1}}{\br_k^H\br_k}$
\State $\bp_{k+1} \gets \br_{k+1} + \beta_{k}\bp_k$
\State $k \gets k + 1$
\EndFor
\end{algorithmic}
\end{algorithm}

@@

The computational complexity of CG is $\mathbb{O}(\sqrt{\kappa}m)$, where $\kappa$ is the generalized specctral condition number of the matrix $\bA$ and $m$ is the number of
non-zero entries in the matrix $\bA$. The mathematical
definition of $\kappa(\bA)$ is
\begin{equation}
\kappa(\bA) = \frac{\lambda_{\textrm{max}}}{\lambda^{+}_{\textrm{min}}}, 
\end{equation}
where $\lambda_{\textrm{max}}$ denotes the largest eigenvalue of $\bA$ and $\lambda^{+}_{\textrm{min}}$ presents the smallest positive eigenvalue. 
Interpreting the computational complexity equation further. Note from Algorithm 1 that the CG method has one major outer loop. In the worst possible case, the amount of iterations needed to converge is
proportional to $\sqrt{\kappa}$. Also notice that the most expensive 
operation that is conducted within each loop is the vector-matrix product, which has complexity $\mathbb{O}(m)$, where $m$ is the number of non-zero entries in the matrix.
The computational complexity of the CG method is therefore 
\begin{equation}
\mathbb{O}(\sqrt{\kappa}m) 
\end{equation}

The best precondtioner would be the preconditioner which makes $\kappa$ unity, i.e. completly
eliminating it from the computational complexity equation. The only choice of $\bM$ which is capable of best way to do this is to chooose as preconditioner the matrix $(\bA)^{-1}$, which is what we would like to determine in the frist place.
If the diagonal entries of $\bA$ are more significant than its off-diagonal entries, then the Jacobian preconditioner is a good preconditioner to use.

>>>>

\section{Conjugate Gradient Method}
The Conjugate Gradient (CG) method was independently discovered by \citet{Hestenes1973} and \citet{Stiefel1952}. They later published a joint paper, which is now considered as the seminal
reference on CG \citep{Hestenes1952}. The iterative CG method is used to solve a particular class of linear systems. The CG method is generally used to solve
\begin{equation}
\label{eq:linear_system}
\bb = \bA\bx,
\end{equation}
where $\bb\in\mathbb{C}^P$ is a known complex column vector of size $P$, $\bx\in\mathbb{C}^P$ is an unknown complex column vector with the same length as $\bb$, and $\bA\in\mathbb{C}^{P\times P}$ is a square positive-definite Hermitian matrix with the appropriate dimensions.  
Moreover, using the CG method to solve Eq.~\eqref{eq:linear_system} will only be computationally advantageous if $\bA$ is also sparse (contain many zero entries).
Using the iterative CG method to solve large sparse linear sytems was popularized by \citet{Reid1971}. A good tutorial on the CG method can be found in \citep{Shewchuk1994}.

%If $\bA$ is a square positive semi-definite Hermitian matrix, then the conjugate gradient method only converges if $\bb$ is in the column range of $\bA$ (cite Lu2016).

\begin{algorithm}
\caption{Conjugate Gradient Method}\label{algo:CG}
\begin{algorithmic}[1]
\State $\br \gets \bA\bx_0 - \bb$
\State $\bp \gets -\br_0$
\For{$k\leq k_{\textrm{max}}$}
\State $\alpha_k \gets \frac{\br_k^H\br_k}{\bp_k^H\bA\bp_k}$
\State $\bx_{k+1} \gets \bx_k + \alpha_k\bp_k$
\State $\br_{k+1} \gets \br_k - \alpha_k\bA\bp_k$
\If{$\|\br_{k+1}\|<\epsilon\|\br_0\|$}
\State break
\EndIf
\State $\beta_{k} \gets \frac{\br_{k+1}^H\br_{k+1}}{\br_k^H\br_k}$
\State $\bp_{k+1} \gets \br_{k+1} + \beta_{k}\bp_k$
\State $k \gets k + 1$
\EndFor
\end{algorithmic}
\end{algorithm}

\subsection{Computational Complexity}
\citet{Kaniel1966} was able to determine convergence bounds for CG using Chebyshev polynomials. A much more in depth analysis of CG convergence can be found in
\citep{Sluis1986}.
The computational complexity of CG is $\mathbb{O}(\sqrt{\kappa}m)$, where $\kappa$ is the generalized specctral condition number of the matrix $\bA$ and $m$ is the number of
non-zero entries in the matrix $\bA$. The mathematical
definition of $\kappa(\bA)$ is
\begin{equation}
\kappa(\bA) = \frac{\lambda_{\textrm{max}}}{\lambda^{+}_{\textrm{min}}}, 
\end{equation}
where $\lambda_{\textrm{max}}$ denotes the largest eigenvalue of $\bA$ and $\lambda^{+}_{\textrm{min}}$ presents the smallest positive eigenvalue. 
Interpreting the computational complexity equation further. Note from Algorithm 1 that the CG method has one major outer loop. In the worst possible case, the amount of iterations needed to converge is
proportional to $\sqrt{\kappa}$. Also notice that the most expensive 
operation that is conducted within each loop is the vector-matrix product, which has complexity $\mathbb{O}(m)$, where $m$ is the number of non-zero entries in the matrix.
The computational complexity of the CG method is therefore 
\begin{equation}
\mathbb{O}(\sqrt{\kappa}m) 
\end{equation}

The best precondtioner would be the preconditioner which makes $\kappa$ unity, i.e. completly
eliminating it from the computational complexity equation. The only choice of $\bM$ which is capable of best way to do this is to chooose as preconditioner the matrix $(\bA)^{-1}$, which is what we would like to determine in the frist place.
If the diagonal entries of $\bA$ are more significant than its off-diagonal entries, then the Jacobian preconditioner is a good preconditioner to use. 
State better that the choice of preconditioner, the value of kappa and what the effect of this would be on the computational complexity of the method.

@@
